Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-04-13 Latex/draft.tex
Found another typo.

\subsection{Method Comparison}
Each of our methods have one general purpose: predict the winner of the game regardless of the point of the game. 
To evaluate our models, we randomly selected 100 games outside of the training data. 
To ensure that the test set represented the actual data, we selected the test set with 50 home wins and 50 away wins, 
and we also made sure there was an even representation of each of the 32 NHL teams. 
We then used each model to predict a winner at various points throughout each game. 
From these predictions on the 100 games, we computed each model's accuracy for each point in the game.

@@

Additionally, there are no privacy concerns with our data as we only collected publicly availalbe NHL data.

>>>>

\subsection{Method Comparison}
Each of our methods has one general purpose: predict the winner of the game regardless of the point of the game. 
To evaluate our models, we randomly selected 100 games outside of the training data. 
To ensure that the test set represented the actual data, we selected the test set with 50 home wins and 50 away wins, 
and we also made sure there was an even representation of each of the 32 NHL teams. 
We then used each model to predict a winner at various points throughout each game. 
From these predictions on the 100 games, we computed each model's accuracy for each point in the game.

@@

Additionally, there are no privacy concerns with our data as we only collected publicly available NHL data.
